### 2022-07-28 main/chapter_2ljets.tex
add event counts for vr-sys

In the looser regions VR-sys-main and VR-sys-OffShell, each variation
reduces to around $10\%$ and remains dominated by the statistical uncertainty.
Although local effects could occur, this is a reasonable indication that these
parameters should not much affect our signal regions.
We therefore apply the variations measured in VR-sys-main to all on-shell
regions,
and the variations measured in VR-sys-OffShell to off-shell regions,
with one parameter coupling all regions for each of
$Q_\textrm{cut}^\textrm{CKKW}$,
\texttt{CSS\_KIN}, and
$S_Q$.

>>>>

In the looser regions VR-sys-main and VR-sys-OffShell,
which receive $1784$ and $7015$ truth events respectively, each variation
reduces to around $10\%$ and remains dominated by the statistical uncertainty.
Although local effects could occur, this is a reasonable indication that these
parameters should not much affect our signal regions.
We therefore apply the variations measured in VR-sys-main to all on-shell
regions,
and the variations measured in VR-sys-OffShell to off-shell regions,
with one parameter coupling all regions for each of
$Q_\textrm{cut}^\textrm{CKKW}$,
\texttt{CSS\_KIN}, and
$S_Q$.
